---
title: "Simple document"
author: "JZ"
date: 9/16/2021
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
---

```{r}
library(tidyverse)
```

I'm an R Markdown document!

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

Let's write a new code chunk.

```{r echo = FALSE}

set.seed(1)

plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)

ggplot(plot_df, aes(x = x)) + geom_histogram()
```

# Section 4

Learning assessment

```{r assesment}
set.seed(1)

try = tibble(
  a = rnorm(500, mean = 1),
  b = a > 0,
  c = abs(a)
)

ggplot(try, aes(x = c)) + geom_histogram()

```

name the chunk by: r name

r, echo/eval/collapse/message = TRUE/FALSE etc

when you click knit, r will restart automatically

rmarkdown::render(input = "name.RMD", output_format = "html_document", output_file = "results/name.html")